---
title: "lobster_exploration"
author: "Charles Hendrickson"
date: "8/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(here)
library(janitor)
```

## 
```{r}
lobsters <- read_csv(here("data","Lobster_Abundance_All_Years_20210412.csv"), na = c("-99999", "")) %>% 
  clean_names() %>% 
  uncount(count)
```

# Create a summary table that finds the total counts (see: n()), and mean carapace lengths of lobsters observed in the dataset by site and year.
```{r}
summary_table <- lobsters %>%
  group_by(site, year) %>% 
  summarize(mean_carapace_length <- mean(size_mm, na.rm = TRUE),
            total_counts = n())

summary_table

# Create a ggplot graph of the number of total lobsters observed (y-axis) by year (x-axis) in the study, grouped (either aesthetically or by faceting) by site

ggplot(data = summary_table, aes(x = year, y = total_counts, color = site))+
  geom_point()+
  geom_line()+
  ggtitle("Total lobster count by year")+
  xlab("Year")+
  ylab("Total Count")

```
# The legal lobster size (carapace length) in California is 79.76 mm.

Create a subset that only contains lobster data from 2020 (note: this should be from the original data you read in, not the summary table you created above)

```{r}
lobster_data_2020 <- lobsters %>% 
  filter(year == 2020)

lobster_data_2020
```


# Write code (you can decide how to do this - there are a number of ways) to find the counts of lobsters observed at each site (only using site as the grouping factor) that are above and below the legal limit. Hint: You may want to add a new column legal that contains “yes” or “no” based on the size of the observed lobster (see dplyr::case_when() for a really nice way to do this), then use group_by() %>% summarize(n()) or dplyr::count() to get counts by group within variables

```{r}
lobster_count <- lobsters %>% 
  mutate(legal_size = case_when(
    size_mm >= 79.76 ~ "yes",
    size_mm <  79.76 ~ "no")) %>%
  count(site) %>% 
  summarize(n())

lobster_count
```















